Comparison of Fast, Hybird Imaging Architectures for Multi-scale, Hierarchical Aperture Arrays

### 2024-06-24 ms.tex
Update on Overleaf.

The specific aperture array examples we consider are the \texttt{SKA-low}, core of the SKA-low (\texttt{SKA-low-core}), \texttt{LAMBDA-I}, \texttt{CASPA} \citep{Luo+2024}, and \texttt{FarView}. The last three are hypothetical interferometers that are being planned for the future. 
% It is assumed that $N_{\textrm{a/s}_m}=N_\textrm{a/s}=256$ (same for each station), $D_\textrm{a}/\lambda=1$, and $D_\textrm{s}/\lambda=17.5$ for each of these arrays, where, the nominal wavelength chosen here is $\lambda=2$~m. The corresponding station filling factor, $f_\textrm{s}=N_\textrm{a/s}\,(D_\textrm{a}/D_\textrm{s})^2$, is 0.836 for all the arrays. ~\texttt{SKA-low-core}, ~\texttt{SKA-low}, ~\texttt{Aus-VLBA-low}, and ~\texttt{IC-VLBA-low} are taken to consist of $N_\textrm{s}=256, 512, 512,$ and 512 stations in an array diameter of $D_\textrm{A}/\lambda=525, 3.25\times 10^4, 1.95\times 10^6$, and $3.9\times 10^6$, respectively. The corresponding array filling factors, defined as $f_\textrm{A}=N_\textrm{s}\,(D_\textrm{s}/D_\textrm{A})^2$, are 0.284, $1.48\times 10^{-4}$, $4.12\times 10^{-8}$, and $1.03\times 10^{-8}$, respectively. 
These parameters for the chosen examples are summarised in Table~\ref{tab:array_params}.

>>>>

The specific aperture array examples we consider are the \texttt{SKA-low}, core of the SKA-low (\texttt{SKA-low-core}), \texttt{LAMBDA-I}, \texttt{CASPA} \citep{Luo+2024}, and \texttt{FarView} \citep{Polidan+2024}. The last three are hypothetical interferometers that are being planned for the future. 
% It is assumed that $N_{\textrm{a/s}_m}=N_\textrm{a/s}=256$ (same for each station), $D_\textrm{a}/\lambda=1$, and $D_\textrm{s}/\lambda=17.5$ for each of these arrays, where, the nominal wavelength chosen here is $\lambda=2$~m. The corresponding station filling factor, $f_\textrm{s}=N_\textrm{a/s}\,(D_\textrm{a}/D_\textrm{s})^2$, is 0.836 for all the arrays. ~\texttt{SKA-low-core}, ~\texttt{SKA-low}, ~\texttt{Aus-VLBA-low}, and ~\texttt{IC-VLBA-low} are taken to consist of $N_\textrm{s}=256, 512, 512,$ and 512 stations in an array diameter of $D_\textrm{A}/\lambda=525, 3.25\times 10^4, 1.95\times 10^6$, and $3.9\times 10^6$, respectively. The corresponding array filling factors, defined as $f_\textrm{A}=N_\textrm{s}\,(D_\textrm{s}/D_\textrm{A})^2$, are 0.284, $1.48\times 10^{-4}$, $4.12\times 10^{-8}$, and $1.03\times 10^{-8}$, respectively. 
These parameters for the chosen examples are summarised in Table~\ref{tab:array_params}.
